Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-25 paper-v1.tex
clean up
fix fig. 1 description

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{\textbf{a}is the core contract of the protocol, it implements a bounty system with the functions listed.
\textbf{b} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
\textbf{c} is the native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin. It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
\textbf{g} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} is the library used by the protocol for secure contract development, with the modules listed.}
\label{fig:contracts}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{\textbf{a} The core contract of the protocol, it implements a bounty system with the functions listed.
\textbf{b} The module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
\textbf{c} The native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin. It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
\textbf{g} Represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} The library used by the protocol for secure contract development, with the modules listed.}
\label{fig:contracts}
\end{figure}
